---
title: "Trailer recommendations exploration"
author: "Gaurav Modi"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
---

```{r setup, echo=FALSE}
suppressPackageStartupMessages({
library(tidyverse)
})
```

This dataset was created by Eva Zhong, based on a movielens experiment 
led by Tahir Sousa.

The dataset contains one observation per user-login. A row appears for any user who viewed one or more movie trailers during their session.  The Algorithm represents a recommendation algorithm they were given, which was randomly assigned on each login.

* `count_total_played` -- total number of movie trailers started during the login session
* `count_rec_played` -- total number of movie trailers played *from a list of recommendations* started during the login session

```{r read-dataset, echo=FALSE}
conditions <- c("ShuffledTopPicks", "TagSimilarity", "PredictedRating", "FilmReleaseDate")
trailer_activities <- readr::read_csv("trailer_activities.csv",
                                          col_types = cols_only(
                                            userId = col_character(),
                                            loginId = col_character(),
                                            Algorithm = col_factor(conditions, ordered = TRUE),
                                            count_total_played = col_integer(),
                                            count_rec_played = col_double()
                                          ))
trailer_activities
```

## Histogram of `count_total_played`

```{r}
g <- ggplot(data = trailer_activities)
```


```{r}
p1 <- g + geom_histogram(mapping = aes(x = count_total_played), binwidth = 5) +
  coord_cartesian(xlim = c(0, 20))

p1
```

## Scatter plots

The relationship between `count_total_played` and `count_rec_played` using:

* geom_point (setting `alpha=0.1`)

```{r}
p2 <- g + geom_point(mapping = aes(x = count_total_played, y = count_rec_played), alpha = 0.1)

p2
```

* geom_jitter

```{r}
p3 <- g + geom_jitter(mapping = aes(x = count_total_played, y = count_rec_played))

p3
```

* geom_count

```{r}
p4 <- g + geom_count(mapping = aes(x = count_total_played, y = count_rec_played))

p4
```


* a `facet_wrap` to split the chart by algorithm

```{r}
p5 <- g + geom_point(mapping = aes(x = count_total_played, y = count_rec_played)) + 
  geom_smooth(mapping = aes(x = count_total_played, y = count_rec_played)) +
  coord_cartesian(xlim = c(0, 50)) +
  facet_wrap( ~ Algorithm)

p5
```

## Summary Statistics

Here are aggregate stats of recommended play actions, grouped by algorithm:

```{r summary-stats}
trailer_activities_summary <- trailer_activities %>% 
  group_by(Algorithm) %>% 
  summarise(
    total_played = n(),
    mean_rec_played = mean(count_rec_played),
    max_rec_played = max(count_rec_played),
    min_rec_played = min(count_rec_played),
    std_err_rec_played = sd(count_rec_played)/sqrt(n())
  )
trailer_activities_summary
```


## Bar chart!

Are the number of observations balanced between the four experimental algorithms?
Build a bar chart of this tibble by Algorithm.

```{r}
g1 <- ggplot(data = trailer_activities_summary)

p6 <- g1 + geom_bar(mapping = aes(x = Algorithm, y = total_played), stat = "identity")

p6
```

* Charting Algorithm by mean_rec_played

```{r}
p7 <- g1 + geom_bar(mapping = aes(x = Algorithm, y = mean_rec_played), stat = "identity")

p7
```


* Standard error plot for each algorithm

```{r}
p8 <- g1 + geom_errorbar(aes(x = Algorithm, ymin = mean_rec_played - std_err_rec_played, ymax = mean_rec_played + std_err_rec_played))

p8
```

    
